# Exploring the data

```{r setup}
setwd("~/src/ganalytics")
library(plyr)
library(ggplot2)
library(stringr)
source('./utility.R')
load('data.Rda')
load('wp_posts.Rda')
load('wp_stats.Rda')
load('posts.Rda')
```

## Check if the data is correct
Let's check the total hits for one given page, and compare with Google Analytics

We'll check the hits for '407 Indonesian textbooks openly available', Google 
Analytics shows 334 page views.
```{r checkdata}
pagetitle = '407 Indonesian textbooks openly available'

# we first select the matching rows, and then sum the visits
sum(tbl[tbl$pageTitle == pagetitle,]$visits)
```

Not sure why it's one more. Let's check for a specific day. 

January 19, 2013, there were 23 visits in total on Google Analytics.
```{r}
sum(tbl[tbl$date == makedate('2013-01-19'),]$visits)
```

Let me try to plot the access to the Indonesian textbook page.
```{r}
ind <- tbl[tbl$pageTitle == pagetitle,]
ggplot(ind, aes(x=date, y=visits)) + geom_point() + geom_smooth()
```

Is there any correlation between length and reading level?
```{r}
ggplot(wp_stats[wp_stats$flesch > 0,], aes(x = flesch, y = length)) + geom_point() + geom_smooth()
```
Doesn't seem so. (For some reason, it doesn't work well on a few foreign songs etc, gives negative level, so I exclude these). 

Showing Flesch-Kincaid level over log(total visits) - no correlation?
```{r}
ggplot(posts[posts$flesch > 0,], aes(x = log(totvisits), y= flesch)) + geom_point() + geom_smooth()
```

Log of total visits over links
```{r}
ggplot(posts, aes(x = log(totvisits), y= links)) + geom_point() + geom_smooth()
```

Log of total visits over comments
```{r}
ggplot(posts, aes(x = log(totvisits), y= num_comments)) + geom_point() + geom_smooth() 
```

Length over total visits
```{r}
ggplot(posts, aes(x = log(totvisits), y= length)) + geom_point() + geom_smooth() 
```
